Push-Pull Signal-Function Functional Reactive Programming

### 2012-11-28 Docs/IFL2012/abstract.tex
Tentative edits to abstract - come back to this later

\begin{abstract}
Functional Reactive Programming is a promising class of systems for writing
interactive and time-dependent programs. Signal-function FRP is a subclass of
these systems which provides advantages of modularity and correctness, but
has proven difficult to efficiently implement.

The abstraction of signal vectors provides the necessary type apparatus to
distinguish components of the input and output of signal functions which benefit
from a push-based implementation from those which benefit from a pull-based
implementation, and to combine both implementation strategies in a single system.

We describe a signal-function FRP system which provides push-based evaluation
for events, pull-based evaluation for signals, and a simple monadic evaluation
interface which permits the system to be easily integrated with one or more
IO systems.
\end{abstract}

>>>>

\begin{abstract}
Functional Reactive Programming is a promising \new{approach} 
\rn{systems -- seems weird to identify it with the implementations... model, approach?} 
for writing interactive and time-dependent programs. Signal-function FRP 
is variant of FRP 
% a subclass of these systems 
which provides advantages in modularity and correctness, but
has proven difficult to implement efficiently.

\textred{The abstraction of signal vectors provides the necessary type apparatus to
distinguish components of the input and output of signal functions which benefit
from a push-based implementation from those which benefit from a pull-based
implementation, and to combine both implementation strategies in a single system.}

\rn{Without understanding it a priori, the above para is hard to
  parse.  How about the following?}

\new{One important implementation trade-off is whether evaluation of a composition 
of signal functions is {\em push-based} or {\em pull-based}.
The {\em signal vector} technique provides a type-level
  description of the inputs and outputs of signal functions, while
  distinguishing} components that benefit from a push-based
implementation from those that benefit from a pull-based
implementation.  This makes it possible to combine both implementation
strategies in a single system.

We describe a novel signal-function FRP system which provides push-based evaluation
for events, pull-based evaluation for signals, and a simple monadic evaluation
interface that permits the system to easily integrate with one or more
IO systems.
\end{abstract}
